---
title: "Vignette"
author: "PForet"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SP 500 R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Easy loading for SP500 stocks data

This package provides some function that allow the user to retrieve the opening, high, low, close and volume levels of the SP500 stocks. Levels can be loaded as a dataframe or, more importantly, as a time serie. 
This package relies on the data provided on Kaggle : see https://www.kaggle.com/camnugent/sandp500

## Whole dataframe

This package allows the user to load the whole dataframe. 'Date' variable has been defined as a Date object, using the 'lubridate' package 
```{r whole}
source("main.R")
whole_dataframe <- all_stocks()
head(whole_dataframe)
```

## Load a stock

You can also load a single stock/value combination. The value to load should be specified using the var_type argument (default is 'Open').
The stock name should be specified. Use /code{SP500_names()} to display all the stocks' names available.
The user can provide starting and ending date, as 'lubridate' dates.

```{r one_df}
start_date <- lubridate::ymd('2014-01-01')
end_date <- lubridate::ymd('2014-01-10')
AAP_Volume <- one_stock.df('AAP', var_type = 'Volume', start = start_date, end = end_date)
AAP_Volume
```
## Load a time serie

Most useful function of this small package. Load a stock value as a time serie, with correct start, end date, and frequency.
Same arguments /code{as one_stock.df}

```{r one_ts}
start_date <- lubridate::ymd('2013-01-01')
AAP_Close <- one_stock.ts('AAP', var_type = 'Close', start = start_date)
plot(AAP_Close)
```

The stock value can then be easily analysed using the usual tools for time serie:

```{r one_ts_analyse}
diff_AAP <- diff(na.omit(AAP_Close))
acf(diff_AAP)
pacf(diff_AAP)
```


